---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# examplepackage

<!-- badges: start -->
<!-- badges: end -->

This is an example R package built for Coursera's Mastering Software Development in R course 2: Building an R Package.

This Package loads, summarizes, and plots US National Highway Traffic Safety Administration's Fatality Analysis Reporting System ([source](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars)), with yearly data on fatal injuries suffered in motor vehicle traffic crashes.

## Installation

You can install from github:

``` r
#> devtools::install_github([path to this repository])
```

## Usage

To load package once installed:

```{r example}
library(examplepackage)
```

The package provides utility functions to:
* access the data in a data frame
* summarize accidents by year
* plot the data by state against a map of the US using the `maps` package. 
Note that if `datadir` argument is not provided, built-in data is loaded automatically.

To access raw data in a data frame:

```{r df}
df = fars_read(filename = 'accident_2013.csv.bz2',   # filename of the built-in dataset for 2013
               datadir = NULL)                       # this loads from the built-in datasets
head(df)
```

To summarize the data:

```{r summary}
fars_summarize_years(c(2013, 2014))
```

To plot the location of fatalities for state indexed 1 for year 2013:

```{r plot}
fars_map_state(1, 2013)
```
